\section{Methodology}
Rather than researching some obscure nook or cranny of mathematics, this project was initially motivated by a desire to try and implement 5 years of education in order to assist with some current real-world problems. From prior work, we hypothesised that there might be quite a handful of such problems within the Danish healthcare sector. As such, we laid the groundwork in March of 2024 by sending out a questionnaire, which can be seen in appendix \autoref{fig:questionnaire_healthcare_personnel}, to \textbf{Rigshospitalet}, \textbf{The Hospital of Hvidovre}, \textbf{The regional Hospital of Northern Jutland}, \textbf{The University Hospital of Aalborg}, \textbf{Hospital unit Midt}, \textbf{The Hospital of Holbæk} and \textbf{The department of orthopaedic surgery at the University Hospital of Odense}. This was met with quite varying responses. Most deemed that answering such a questionnaire would be an abhorrent misuse of their personnel's limited time. This, admittedly, left us a bit discouraged. However, we still received a total of 39 answers from medical professionals.
\\
The questionnaire was two questions\footnote{With the option to add your name and/or mail for possible further inquiry.}:
\begin{itemize}
    \item What is the biggest and most frequent problem in your daily life as a healthcare professional?
    \item What do you think is the biggest and most frequent problem in the daily life of your patients?
\end{itemize}
The responses about the daily life and tasks of healthcare professionals varied significantly, but they could likely be summarised as a general dissatisfaction with the understaffed and underfunded state of the healthcare sector.
\\
Many complained about the intricate journaling processes - documenting the patients' progress, reading through a lot of unnecessary documentation and documenting the same thing twice. 
\\
There was a plethora of replies criticising the IT systems currently in place. Complaining that they either didn't work, were too slow or kept crashing. Additionally, one respondee noted that they have a lot of programs that advertise useful functionality, but because they aren't integrated with all the other individual solutions, the healthcare staff end up having to open multiple programs documenting the same data many times over.
\\
Some mentioned that there are a lot of wrongful queries to the emergency line that have to be redirected. It was also added that a filter or automatic redirection might save a lot of critical time.
\\
Finally, the vast majority of responses were aimed at a lack of resources. This included being understaffed, resulting in insufficient time to care for patients and individual staff members being assigned too many tasks. Additionally, there was a shortage of critical inventory, such as bed space and essential medical equipment. Moreover, the existing equipment was often old or outdated due to budget cuts.
