\section{Discussion}
Administrative tasks are an evergrowing burden on the Danish healthcare sector\cite{Information-increase-in-admin, Dansk-Erhverv-increase-in-admin, OL-increase-in-admin, Altinget-increase-in-admin}. In a 2023 working conditions investigation conducted by the Danish "Overl\ae geforening"~\cite{OL-increase-in-admin}, they saw that out of \(2,593\) respondents  \(66\%\) said the main reason for them not managing all their clinical tasks, was administrative tasks getting in the way. Furthermore, an analysis made by "Dansk Erhvev"~\cite{Dansk-Erhverv-increase-in-admin} in 2017 saw, over the prior decade, an increase of \(30\%\) in the administrative workforce of the Danish healthcare sector. Additionally, multiple Danish articles, one from "Altinget"~\cite{Altinget-increase-in-admin} and another from "Information"~\cite{Information-increase-in-admin} to mention a couple, reflect through interviews the frustration of Danish healthcare personnel in having to manage an overflow of administrative tasks.
\\
\\
This entire project stems from a genuine desire to employ the theoretical groundwork laid by a master's education in a real-world scenario in the interest of alleviating everyday repetitive or tedious tasks, such as the administrative burden of the Danish healthcare sector. 
\\
With our competencies built off a computer science background, we have sought to accomplish this by: firstly, writing a readable, easy-to-maintain codebase, which could lay the foundation for future development; secondly, analysing the problem at hand and finding and understanding a well-suited, theoretical formulation for it.

\subsubsection*{The dedication to good code}
Although time did not permit us to write a full theory section, we have nevertheless tried to adhere stringently to the principles of clean code, practised by, amongst others, Martin~\cite{Clean-Code}. In particular, we have spent a considerable amount of time dedicated to the naming of variables, structures, and functions in order to comply with good naming conventions.
\\
We have tried to keep any function no longer than a \(100\) lines, following NASA's design principles~\cite{Wiki-NASA-code} for safety-critical and easier debugging. Furthermore, to the best of our abilities, we have ensured that our functions fulfil a sole purpose and nothing more. On the same initiative, we have designed functions to take in a bare minimum of parameters, of course excluding toggleable configurations, which, without a Graphical User-Interface (GUI) that could service the end-users' preferences, we have kept as a \texttt{config.toml} file.
\\
We have spent numerous hours thinking and discussing with colleagues what structure might best represent the data for visualising the \acrshort{ouh} taskboard. And if we might add, we believe we have arrived at a great solution which acts as a medium between the format of \acrshort{ouh}'s data and a \texttt{panda}'s \texttt{dataframe} while also enabling update, extract and overwrite functionality along methods for handling some peculiar edge-cases.
\\
Additionally, we have made sure to utilise modern version control tools such as \texttt{git}. Specifically, we have made extensive use of \texttt{Github}'s 'projects' and 'actions' functionally, which has greatly supported our coding- and continuous integration workflow. Moreover, as our codebase is developed in Python, we have guaranteed that it stays \texttt{pep8}\cite{pep8} compliant by using the built-in \texttt{ruff} extension for Visual Studio Code, which served as our Integrated Development Tool (IDE). The configuration of which can be seen in our \texttt{pyproject.toml} files.

\subsubsection*{The choice of theoretical formulation}
In choosing our courses throughout our education at \acrshort{dtu}, we have had a strong inclination towards \acrshort{ai} and algorithmic courses; as such, we have had relatively little experience (5 ECTS if one were to be pedantic) within the field of \acrshort{or}. Therefore, we found it incredibly interesting and exciting to work with the \acrshort{bsat} formulation. As \acrshort{bsat} is NP-complete, we have dabbled a bit in this theory before, yet we have in no way the same competencies as if we had taken the full suite of \acrshort{or} courses at \acrshort{dtu}. Additionally, it was a pleasant revisit with the tree representation, as employed by the methods behind \acrshort{sat} solvers (as detailed in \autoref{sec:Constraint_Programming}), where our algorithmic intuition could come into play.
\\
After further considering our analysis of the Assignment Problem, we believe it might be less infeasible than at first presented. Such a solution would still require running an algorithm for each day in the timeframe. Yet, in theory, if developed with zealous consideration for peculiar constraints, such as those posed by the "Rygvagt" task, we believe it could be solved with the Assignment Problem formulation.
\\
Although the Assignment Problem formulation, to some degree, is more algorithmically inclined than its \acrshort{bsat} counterpart, due to the many intricacies in designing a software backend, we still believe we made the right choice with the \acrshort{bsat} formulation. A key factor, as we touched upon in \autoref{sec:scheduling-assistant}, is the abstraction required for the Scheduling Assistant Tool to serve the end-user properly. It seems like the intricacies connected with developing a solution using the Assignment Problem formulation would serve as a significant hindrance. Despite it being an interesting challenge from a software and algorithm perspective, we fear it would distract too greatly from designing the best possible abstraction, which ultimately acts as the foundation for the best possible user interface (UI) to serve the end-user. As such, it seemed at odds with our goal of aiding the Danish healthcare personnel in their everyday tasks.
\\
Similarly, the same can be said for the \acrshort{ga} scheme. While we never got so far as to write actual code, we still spent many a week pondering and discussing with colleagues how we could employ an optimisation method, such as the \acrshort{ga} scheme, to solve the scheduling task. In the end, we deemed that the \acrshort{ga} approach has the same shortcomings as that of the Assignment Problem formulation. Although it is a formally accepted \acrshort{ai} method, and it would be interesting to experiment with from an academic perspective, it cannot make any guarantees of finding a solution. Thus, modelling a \acrshort{ga} would be as great of a hindrance as developing a functioning algorithm using the Assignment Problem formulation.
\\
On the contrary, by electing the \acrshort{bsat} formulation, we could make use of the Google OR-Tools package, which, as detailed in \autoref{sec:translating-constraints}, allows for some seamless translations of informal logic to working code. As a result, this choice would have allowed for focusing on the most critical aspects of developing a Scheduling Assistant Tool which could best support the end-user.

\subsubsection*{The challenges presented by the Digital Taskboard}
We started this project by agreeing to provide \acrshort{ouh} with a digital replacement for their current, manually transcribed taskboard (as detailed in \autoref{sec:Digital-Taskboard}). While true that this problem, on its own, couldn't provide a sufficient academic foundation for a Master's thesis in AI, we were nevertheless surprised by the scope of the problem and ultimately underestimated just how cumbersome\footnote{Which, to her great credit, our supervisor had actually warned us about.} of a task digitalising the taskboard could be.
\\
\\
The greatest obstacle for this part of the project was undoubtedly our inability to fulfil the role of IT consultant in conjunction with the lack of technical insight at \acrshort{ouh}.
\\
More precisely, the difficulty was twofold. Firstly, we have no prior, real experience in the role of IT consultant nor in interacting with an actual 'client' (in our case, \acrshort{ouh}). Secondly, \acrshort{ouh} is a clinical institution, and therefore, they are in no way at fault; nevertheless, they couldn't provide much insight into the more technical nuances of their organisation. This less-than-perfect cocktail is the reason why we, from the onset, failed to pinpoint the critical issues, which would later become technical bottlenecks. Here, we, in particular, recall the desire from \acrshort{ouh} for the digital taskboard to have online updating capabilities. At one of the very first meetings, we had with multiple staff representatives\footnote{It consisted of us, someone from IT, the head nurse of the department and our contact, a project and development nurse.}, we all agreed that this feature was necessary if the digital taskboard should replace the current physical whiteboard. If any one party had noticed the discrepancy in formatting between the spreadsheet where the names are updated and the spreadsheet where the names are initially extracted, we could have quickly determined whether the solution was even feasible or discussed how we should address the issue.
\\
Although this case best exemplifies our inability to assume the role of IT consultant, we nevertheless got to experience the eternal headache of consultancy, namely, the client's own confusion as to what they need. As illustrated in \autoref{fig:infographic}, the vast majority of our workflow was a deeply iterative process. One half consisted of working on some technical issue and then either realising there was some kind of inconsistency or, what we would consider a, bug in their data and then presenting it for \acrshort{ouh}. For the other half, we implemented some feature which they had informed us would certainly wrap up the project, just to be told, when presenting the finalised version, that this other additional feature would, in reality, also be quite nice to have.
\\
Despite our many troubles developing software for real, authentic humans rather than in the neat, manageable setting presented at \acrshort{dtu}, when it came down to the actual implementation of code, everything wasn't precisely "la vie en rose" either.
\\
\\
At a glance, digitalising the taskboard seemed no more complex than merging two 2D datasets, and we are still convinced it could have been were it not for \acrshort{ouh}'s currently in-place payroll and calendar overview system, HosInfo, serving as an ever-persistent thorn in our side. While the HosInfo implementation could be criticised plentily for its sluggish and featureless backend\footnote{Which we admittedly never had access to but only have seen in parsing when been guided through the system by the \acrshort{ouh} staff.}, beyond the shadow of a doubt, our biggest gripe with it was its data handling or, rather, lack thereof. Not only does HosInfo make \acrshort{ouh}'s data nearly inaccessible by storing text data as pictures, but they also enforce no data formatting on their users. Additionally, rather than designing a solution capable of serving the greater planning effort at \acrshort{ouh}, they have delivered a solution to a smaller subproblem while completely disregarding even the slightest notion of compatibility with the rest of \acrshort{ouh}'s IT environment.
\\
Such software makes it nigh impossible for \acrshort{ouh}, not even to mention other external providers such as ourselves, to develop other solutions that need access to their data without forcing the end user to document everything many times over.
\\ 
However, HosInfo isn't the only third-party provider that is guilty of contributing to \acrshort{ouh}'s messy, tangled, and, at the same time, disconnected IT stack. We can only speculate on the reasons behind how it ends up as such. It might be due to the Danish and European procurement legislation~\cite{Udbudsloven, EU-Procurement-Legislation} limiting Danish clinical institutions in their choice of third-party provider. Just as likely, and as aforementioned, these clinical institutions aren't tech companies, and therefore, it would be terribly na\"ive to expect them to be able to perfectly resolve the finer technical details of all their administrative challenges. Nevertheless, it culminates in a system comprising a slew of individual IT solutions, which cannot share data nor benefit from what each other provides.
\\
Trying to work around this constant impediment is perfectly summarised by this single response to our questionnaire, which loosely translated into English would be:
\begin{center}
 \textit{We have many systems that can do quite a lot, but not always in conjunction with each other, and most of the time, you have to work across several applications.}
\end{center}
While (our interpretation of) this statement perfectly encapsulates our immense frustration after six months of efforts of working with (or around) the Danish healthcare sector's IT, we can still scarcely imagine having to work with it on a daily basis. Therefore, we thoroughly believe that a more cohesive and all-encompassing platform would be the right move.
\\
We envision a cloud-based platform with data formatting requirements which can serve data to the correct users. Such a platform should have a single standardised UI  and allow the administrative workers to extract and log data for their corresponding hospitals (or other clinical facilities). It should facilitate an API allowing approved independent third-party providers to create individual software solutions that could work off of this platform. Such a platform would immediately eliminate any need to log data multiple times, as it would all be gathered in one place. Furthermore, if such a platform enforced a UI design guide onto third-party providers and required them to implement their solution onto the platform, it would save the healthcare personnel from having multiple credentials and remembering different layouts for each and every single individual application.
\\
This idea would require a lot from the IT sectors of the Danish healthcare sector; in turn, we also hope that it would be easier to maintain if all of it was gathered onto a single platform, with the single uniform goal of facilitating more seamless implementation of IT solutions.
\\
However, this isn't exactly 'new tech', as "Danske Regioner" in 2024 proposed a 'Danish Healthcare Cloud'~\cite{Den-Reg-digitalisation}. The referenced note touches upon many of the same topics as we have just detailed. Rather than feeling amiss for only arriving at the same conclusion as somebody else had found way before us, we will instead let it enforce our belief that such a restructuring wouldn't simply be an improvement; it is a requirement.
\\
\\
This brings us nicely along to our next point, for although, in all likelihood, we wouldn't be qualified to implement such a platform, we did attempt to build The Scheduling Assistant tool, which we believe could have been a good starting point for \acrshort{ouh}, at least.
\\
As mentioned, digitalising the \acrshort{ouh} taskboard didn't seem academically sufficient; therefore, we also pursued the scheduling task. We believed that we could implement this side-by-side with the digital taskboard. While we still think it technically feasible, as it has been done before~\cite{you-but-better} (and to a way greater extent), much like for the digital taskboard, we ran into multiple unforeseen difficulties.

\subsubsection*{The challenges presented by the Scheduling Task}
Whereas for the digital taskboard, the complications were primarily technical in nature, for the scheduling task, the bottleneck was very much the human factor.
\\
Firstly, most of the data required for planning a correct schedule isn't documented anywhere at \acrshort{ouh}; it is simply some information that the administrative workers have learned through their practice. For us, acting as an external provider, this immediately complicates everything. If we are to develop a system or solution that could alleviate some of their more tedious tasks, that information is critical. However, for them to provide us with that, they must first halt their daily jobs and instead spend their time documenting this information. This is neither in the interest of the administrative workers, as we are only piling on to their already stacked workload, nor is it in the interest of their bosses because we don't provide any immediate value. Thus, we ended up working solely on a very small subproblem of the greater planning effort. This situation is obviously not ideal from the perspective of an engineer, as one would prefer to address the most challenging issues first to determine whether the modelling is feasible. From there, we could then scale down to smaller problems.
\\
\\
Yet, a huge topic for discussion concerning the scheduling task, regardless of the modelling complexity, is the interface design. As we touched upon at the end of \autoref{sec:scheduling-assistant}, the interface is in no way straightforward to design. Still, it is crucial to get it right in order for a solution to the scheduling task to be viable. 
\\
As we mentioned, the key is to design an interface which provides a seamless transition from informal constraints to coding logic. It is clear to us that some kind of abstraction is required; we are just uncertain as to exactly what shape it would take. However, we believe this abstraction must be found in collaboration with the end user. It should be designed based on iterative testing of a prototype. From there, it can be derived what constraints are easily defined as shown with \autoref{tab:Agent-Chart}, \autoref{tab:Agents}, \autoref{tab:Rolling-Chart} and \autoref{tab:Tasks}, and whether more convoluted translations could be taught to the end user, or if that would ultimately mean the interface had failed to do its job. Here, we, in particular, consider the task which had the same name for every day of the week, except for a single day where it was slightly more complex requiring two agents instead of one. We ended up modelling this as two distinct tasks, but maybe the final interface should have some kind of toggle where the end user could specify just how many agents that specific task requires. This is just one example, and we believe that for a bigger problem, this could not only have been an intricate subject for research but also a very interesting one.

\subsubsection*{A last dicth effort: The Schedule Validator}
Regrettably, we failed to realise till it was probably too late that we hadn't accumulated enough goodwill with the administrative staff, which could provide us with the critical data. 
\\
While we had looked at the issue presented by the greater planning effort at \acrshort{ouh} through a goal- and solution-oriented lens, we missed the smaller pieces that make up the larger picture.
\\
The planning and administrative staff had initially revealed to us that they spent a significant amount of time simply checking whether their final schedule adhered to management's plan. We were far too quick to dismiss this problem, as we saw it would be made redundant by a scheduling assistant tool, which could simply plan a correct schedule the first time around.
\\
However, seen through the wise glasses of hindsight, this was an incredibly novice approach for multiple reasons. Firstly, it is probably always good advice to at least acknowledge the concerns of your stakeholders. Secondly, we simply failed to consider a test-driven implementation. We were so blinded by focusing on implementing a schedule planner that could adhere to their constraints and plan a correct schedule that we didn't consider there could exist methods other than \acrshort{cp} to confirm the validity of the final schedule. This check would be a valuable, if not necessary, addition to any solution which is designed to serve the full planning procedure. Thirdly, it didn't help us gain the trust of the administrative staff, who were, and still are, the only ones who could provide us with the information necessary to create a functioning scheduling assistant tool. 
\\
As detailed in \autoref{sec:schedule-validator}, we eventually saw the light and started implementing this validator tool and if given the time, we would still like to finalise this project, even if only to contribute something to \acrshort{ouh}. However, we cannot help but question whether it is a good idea. To be frank, we are afraid of being another attempt in a long line of software implementations that had insisted they keep on their floaties - rather than ever letting them try to swim on their own.
\\
More specifically, after having criticised the current state of the Danish healthcare sector's IT plentily, we see the hypocrisy in simply adding another piece of disjointed software, which they would need to learn to use and which does not function in tandem with the rest of \acrshort{ouh}'s tech stack.

\subsubsection*{Scalability}
We are still convinced that the approach we have laid out would work just as well in other clinical departments and, quite possibly, in smaller clinical institutions. From our conversations with \acrshort{ouh} staff, even though multiple digital tools intended for shift registration exist, few, if any, ever truly automate the scheduling process; in practice, almost everyone produces the final schedules by hand. This arrangement may be tolerable in larger hospitals, where dedicated administrative personnel can handle the greater planning effort. However, from what we have heard (heard second-hand), some smaller clinics lack the budget or manpower for specialised planners, leaving senior doctors to assemble these schedules themselves. In such settings, a scheduling solution that can handle most of the tedious work would, arguably, be even more beneficial. Obviously, any successful rollout still depends on stakeholder acceptance and some willingness to integrate new technology into existing routines. Still, there is next to nothing in our design that prevents it from being applied to other environments once the local constraints have been formalised.

\subsubsection*{GDPR considerations}
A final yet crucial consideration is the security and privacy of the data being processed. Any solution handling personnel schedules or patient-related documentation must comply with appropriate regulations, such as GDPR~\cite{EU-GDPR}, which requires clear definitions of data ownership and responsible data controllers. While we certainly do not claim the expertise to deliver a fully GDPR-compliant system, we still acknowledge that any production-ready tool must incorporate both encryption standards and access controls in order to guarantee the confidentiality of the stored data. However, this would, in turn, add further to \acrshort{ouh}'s already stacked workload, as they would be required to define protocols for system access, user actions, logging and more. If such regulations are ignored and the developers fail to implement the necessary safeguards, regardless of how seamlessly designed or efficiently optimised the system is, it ultimately risks falling short due to legal and ethical complications - potentially resulting in a final product that is never adopted.
\\
\\
All things considered, no matter the software implementation, a rigorous mixture of technical skills, stakeholder and project management, and thoughtfully designed UI is necessary for it to be adapted successfully into the Danish healthcare sector. In turn, if the sector actually desires modernisation through the automation of their more tedious and less clinical tasks, they must be prepared to take the necessary steps for GDPR compliance, data formatting and procedural restructuring. 